---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
options(width = 80)

knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "Readme_files/"
)

if (FALSE) {
pkgs = c("here", "opalr", "DSI", "DSOpal", "dsBaseClient")
for (pkg in pkgs) {
  if (! requireNamespace(pkg, quietly = TRUE))
    install.packages(pkg, repos = c(getOption("repos"), "https://cran.obiba.org"))
}
devtools::install(quiet = TRUE, upgrade = "always")

## Install packages on the DataSHIELD test machine:
surl     = "https://opal-demo.obiba.org/"
username = "administrator"
password = "password"

opal = opalr::opal.login(username = username, password = password, url = surl)

check1 = opalr::dsadmin.install_github_package(opal = opal, pkg = "dsCWB", username = "schalkdaniel", ref = "main")
if (! check1)
  stop("[", Sys.time(), "] Was not able to install dsCWB!")

check2 = opalr::dsadmin.publish_package(opal = opal, pkg = "dsCWB")
if (! check2)
  stop("[", Sys.time(), "] Was not able to publish methods of dsCWB!")
}

opalr::opal.logout(opal)
```

[![Actions Status](https://github.com/schalkdaniel/dsCWB/workflows/R-CMD-check/badge.svg)](https://github.com/schalkdaniel/dsCWB/actions) [![License: LGPL v3](https://img.shields.io/badge/License-LGPL%20v3-blue.svg)](https://www.gnu.org/licenses/lgpl-3.0) [![codecov](https://codecov.io/gh/schalkdaniel/dsCWB/branch/main/graph/badge.svg?token=0K9P2WBKNH)](https://codecov.io/gh/schalkdaniel/dsCWB)

# Component-wise boosting for DataSHIELD

The package provides functionality to conduct and visualize component-wise boosting on decentralized data. The basis is the [DataSHIELD](https://www.datashield.org/) infrastructure for distributed computing. This package provides the calculation of the [__component-wise boosting__](https://www.tandfonline.com/doi/abs/10.1198/016214503000125). Note that DataSHIELD uses an option `datashield.privacyLevel` to indicate the minimal amount of numbers required to be allowed to share an aggregated value of these numbers. Instead of setting the option, we directly retrieve the privacy level from the [`DESCRIPTION`](https://github.com/schalkdaniel/dsCWB/blob/master/DESCRIPTION) file each time a function calls for it. This options is set to 5 by default.


## Installation

At the moment, there is no CRAN version available. Install the development version from GitHub:

```{r,eval=FALSE}
remotes::install_github("schalkdaniel/dsCWB")
```

#### Register methods

It is necessary to register the assign and aggregate methods in the OPAL administration. These methods are registered automatically when publishing the package on OPAL (see [`DESCRIPTION`](https://github.com/schalkdaniel/dsCWB/blob/main/DESCRIPTION)).

Note that the package needs to be installed at both locations, the server and the analysts machine.


## Usage

```{r}

q()
R
devtools::load_all()

library(DSI)
library(DSOpal)

surl     = "https://opal-demo.obiba.org/"
username = "administrator"
password = "password"

builder = newDSLoginBuilder()

builder$append(
  server   = "server1",
  url      = surl,
  user     = username,
  password = password,
  table    = "CNSIM.CNSIM1"
)
builder$append(
  server   = "server2",
  url      = surl,
  user     = username,
  password = password,
  table    = "CNSIM.CNSIM2"
)
builder$append(
  server   = "server3",
  url      = surl,
  user     = username,
  password = password,
  table    = "CNSIM.CNSIM3"
)
connections = datashield.login(logins = builder$build(), assign = TRUE)
datashield.symbols(connections)

datashield.assign(connections, "Dclean", quote(dsNaRm("D")))
datashield.symbols(connections)

dsBaseClient::ds.dim("D")
dsBaseClient::ds.dim("Dclean")

symbol = "Dclean"
target = "LAB_TSC"
feature_names = setdiff(dsBaseClient::ds.names("D", connections)[[1]], target)

time = Sys.time()
cwb = dsCWB(connections, "Dclean", target, feature_names, mstop = 10L,
  val_fraction = 0.1, patience = 5L, eps_for_break = 0, seed = 31415L)
time = Sys.time() - time

l = cwb$getLog()
l$minutes = as.numeric(difftime(l$time, l$time[1], units = "mins"))

library(ggplot2)

ggplot(l, aes(x = minutes)) +
  geom_line(aes(y = risk_train, color = "Train risk")) +
  geom_line(aes(y = risk_val, color = "Val risk"))

table(l$bl)
table(l$effect_type)

newdata = na.omit(read.csv("~/Downloads/data.csv"))[1:10, ]
cwb$predictIndividual(newdata)
pred = cwb$predict(newdata, "server1")
truth = newdata[[target]]

dval = data.frame(pred, truth)
ggplot(dval, aes(x = pred, y = truth)) + geom_point()

pdata = cwb$featureEffectData("LAB_TRIG")

ggplot(pdata, aes(x = value, y = pred, color = server, linetype = effect_type)) +
  geom_line()







cwb$get
mstop = 20L
learning_rate = 0.1
df = 5
nknots = 20L
ord = 3L
derivs = 2L
val_fraction = 0.1
patience = 5
eps_for_break = 0.1
positive = NULL
seed = 31415
trace = TRUE

datashield.logout(connections)
```
